Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-03 output/latex/manuscript.tex
latex: remove orcid and social media handles

\begin{itemize}
\item
  \textbf{Milton Pividori}\textsuperscript{1,2} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social}
\item
  \textbf{Sumei Lu}\textsuperscript{3}
\item
  \textbf{Binglan Li}\textsuperscript{4} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-0103-6107}{0000-0002-0103-6107}
\item
  \textbf{Chun Su}\textsuperscript{3} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6388-8666}{0000-0001-6388-8666}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/sckinta}{sckinta}
\item
  \textbf{Matthew E. Johnson}\textsuperscript{3}
\item
  \textbf{Wei-Qi Wei}\textsuperscript{5}
\item
  \textbf{Qiping Feng}\textsuperscript{5} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6213-793X}{0000-0002-6213-793X}
\item
  \textbf{Bahram Namjou}\textsuperscript{6}
\item
  \textbf{Krzysztof Kiryluk}\textsuperscript{7} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-5047-6715}{0000-0002-5047-6715}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/kirylukk}{kirylukk}
\item
  \textbf{Iftikhar Kullo}\textsuperscript{8}
\item
  \textbf{Yuan Luo}\textsuperscript{9}
\item
  \textbf{Blair D. Sullivan}\textsuperscript{10} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7720-6208}{0000-0001-7720-6208}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bdsullivan}{bdsullivan}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/blairdsullivan}{blairdsullivan}
\item
  \textbf{Benjamin F. Voight}\textsuperscript{11,12,13} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6205-9994}{0000-0002-6205-9994}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bvoight}{bvoight}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/bvoight28}{bvoight28}
\item
  \textbf{Carsten Skarke}\textsuperscript{13} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-5145-3681}{0000-0001-5145-3681}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/CarstenSkarke}{CarstenSkarke}
\item
  \textbf{Marylyn D. Ritchie}\textsuperscript{1} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-1208-1720}{0000-0002-1208-1720}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/MarylynRitchie}{MarylynRitchie}
\item
  \textbf{Struan F.A. Grant}\textsuperscript{3,14,15,1} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-2025-5302}{0000-0003-2025-5302}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/STRUANGRANT}{STRUANGRANT}
\item
  \textbf{Casey S. Greene}~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2} \\
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8713-9213}{0000-0001-8713-9213}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/cgreene}{cgreene}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/GreeneScientist}{GreeneScientist}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@greenescientist}{@greenescientist@genomic.social}
\end{itemize}

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
{\Letter} --- Correspondence possible via GitHub Issues
or email to
Casey S. Greene \textless casey.s.greene@cuanschutz.edu\textgreater.

@@

This study was funded by:
the Gordon and Betty Moore Foundation (GBMF 4552 to C.S. Greene; GBMF 4560 to B.D. Sullivan),
the National Human Genome Research Institute (R01 HG010067 to C.S. Greene, S.F.A. Grant and B.D. Sullivan; K99 HG011898 and R00 HG011898 to M. Pividori; U01 HG011181 to W. Wei),
the National Cancer Institute (R01 CA237170 to C.S. Greene),
the Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765 to C.S. Greene),
the National Institute of Aging (R01AG069900 to W. Wei),
the National Institute of General Medical Sciences (R01 GM139891 to W. Wei);
the National Heart, Lung, and Blood Institute (R01 HL163854 to Q. Feng);
the National Institute of Diabetes and Digestive and Kidney Diseases (DK126194 to B.F. Voight);
the Daniel B. Burke Endowed Chair for Diabetes Research to S.F.A. Grant.

>>>>

\begin{itemize}
\item
  \textbf{Milton Pividori}\textsuperscript{1,2}
\item
  \textbf{Sumei Lu}\textsuperscript{3}
\item
  \textbf{Binglan Li}\textsuperscript{4}
\item
  \textbf{Chun Su}\textsuperscript{3}
\item
  \textbf{Matthew E. Johnson}\textsuperscript{3}
\item
  \textbf{Wei-Qi Wei}\textsuperscript{5}
\item
  \textbf{Qiping Feng}\textsuperscript{5}
\item
  \textbf{Bahram Namjou}\textsuperscript{6}
\item
  \textbf{Krzysztof Kiryluk}\textsuperscript{7}
\item
  \textbf{Iftikhar Kullo}\textsuperscript{8}
\item
  \textbf{Yuan Luo}\textsuperscript{9}
\item
  \textbf{Blair D. Sullivan}\textsuperscript{10}
\item
  \textbf{Benjamin F. Voight}\textsuperscript{11,12,13}
\item
  \textbf{Carsten Skarke}\textsuperscript{13}
\item
  \textbf{Marylyn D. Ritchie}\textsuperscript{1}
\item
  \textbf{Struan F.A. Grant}\textsuperscript{3,14,15,1}
\item
  \textbf{Casey S. Greene}~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}
\end{itemize}

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
{\Letter} --- Correspondence possible via email to
Casey S. Greene \textless casey.s.greene@cuanschutz.edu\textgreater.

@@

This study was funded by:
the Gordon and Betty Moore Foundation (GBMF 4552 to C.S. Greene; GBMF 4560 to B.D. Sullivan),
the National Human Genome Research Institute (R01 HG010067 to C.S. Greene, S.F.A. Grant and B.D. Sullivan; K99 HG011898 and R00 HG011898 to M. Pividori; U01 HG011181 to W. Wei),
the National Cancer Institute (R01 CA237170 to C.S. Greene),
the Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765 to C.S. Greene),
the National Institute of Aging (R01AG069900 to W. Wei),
the National Institute of General Medical Sciences (R01 GM139891 to W. Wei);
the National Heart, Lung, and Blood Institute (R01 HL163854 to Q. Feng);
the National Institute of Diabetes and Digestive and Kidney Diseases (DK126194 to B.F. Voight);
the Daniel B. Burke Endowed Chair for Diabetes Research to S.F.A. Grant;
the Robert L. McNeil Jr.~Endowed Fellowship in Translational Medicine and Therapeutics to C. Skarke.
